Starcode: sequence clustering based on all-pairs search

### 2014-11-03 doc/document.tex
Document: Added command-line tables.

\subsection{Benchmark conditions}
All the tests were performed on a 16-core dual-processor
Intel Xeon E5-2687W v2 system with 256~GB of DDR3-RAM at 1866~Mhz

@@

@@

%\begin{table}[h]
%\centering
%\caption{Software execution parameters (benchmark 1)}
%\resizebox{\columnwidth}{!}{
%\begin{tabular}{|l|l|}
%    \hline
%    starcode & \texttt{-d3 -t12 -s}\\ \hline
%    CD-HIT 4.6.1 & \texttt{cd-hit-est -n 7 -c .925 -T 12 -M 0 -r 0 -A 40}\\ \hline
%\end{tabular}
%}
%\label{tab:params1}
%\end{table}

@@

\begin{table}[h]
\centering
\caption{Summary of the biological datasets used for benchmarking.
All the datasets are Illumina reads.}
\begin{tabular}{|l|l|l|l|}
    \hline
    \textit{dataset}   & \textit{read count} &
    \textit{read length} & \textit{type} \\ \hline
    dataset 1 & 16,457,527   & 50  & single      \\ \hline
    dataset 2 & 127,675,537  & 50  & single      \\ \hline
    dataset 3 & 2,460,226    & 100  & paired-end \\ \hline
\end{tabular}
\label{tab:biobench_properties}
\end{table}

@@

\begin{table}[h]
\centering
\caption{Running time (in seconds) of the software on three biological
datasets. Runs longer than 10 days were interrupted. A dash indicates
that the software cannot be used for this dataset.}
\begin{tabular}{|l|l|l|l|}
    \hline
    \textit{software}   & \textit{dataset 1} &
      \textit{dataset 2} & \textit{dataset 3} \\ \hline
    starcode   & 171         & 2,898       & 44    \\ \hline
    seed       & 135,959     & 60,374      & -     \\ \hline
    sidesort   & 632,168     & $>$ 10 days & -     \\ \hline
    rainbow    & -           & -           & 306   \\ \hline
    cd-hit-est & $>$ 10 days & 512,591     & -     \\ \hline
\end{tabular}
\label{tab:biobench_runtime}
\end{table}

@@

\begin{table}[h]
\centering
\caption{Memory usage (in Gb).}
\begin{tabular}{|l|l|l|l|}
    \hline
    \textit{software}   & \textit{dataset 1} &
      \textit{dataset 2} & \textit{dataset 3} \\ \hline
    starcode   & 9.4 & 30.9 & 5.2 \\ \hline
    seed       & 4.1 & 53.9 & -   \\ \hline
    sidesort   & 1.9 & 13.9 & -   \\ \hline
    rainbow    & -   & -  & 0.5   \\ \hline
    cd-hit-est & 3.8 & 28.5 & -   \\ \hline
\end{tabular}
\label{tab:biobench_memory}
\end{table}

>>>>

@@

\subsection{Benchmark conditions}
All the tests were performed on a 16-core dual-processor
Intel Xeon E5-2687W v2 system with 256~GB of DDR3-RAM at
1866~Mhz. Command-line parameters were set equivalently in all
softwares to run in single-core mode allowing up to 3 mismatches for
input sequences of length 50. Execution options used in simulation and
real datasets are summarized in Table \ref{tab:params1} and Table
\ref{tab:params2}, respectively.

\begin{table}[h]
\centering
\caption{Software execution options used in simulation benchmark.}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{l|l}
    \bf{software} & \bf{execution options}\\
    \hline
    starcode & \texttt{starcode -d3}\\
    slidesort & \texttt{slidesort\_v2 -d 3 -t E -c DNA}\\
    CD-HIT 4.6.1 & \texttt{cd-hit-est -n 9 -c 0.9 -M 0 -r 0}\\
    SEED & \texttt{SEED --mismatch 3}\\
\end{tabular}
%}
\label{tab:params1}
\end{table}

\begin{table}[h]
\centering
\caption{Software execution options used in real data benchmark.}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{l|l}
    \bf{software} & \bf{execution options}\\
    \hline
    starcode & \texttt{starcode -d3}\\ 
    slidesort & \texttt{slidesort\_v2 -d 3 -u -t E -c DNA}\\
    CD-HIT 4.6.1 & \texttt{cd-hit-est -n 8 -c 0.94 -M 0}\\
    SEED & \texttt{SEED --mismatch 3 --shift 3}\\ 
\end{tabular}
%}
\label{tab:params2}
\end{table}

@@

@@

\begin{table}[h]
\centering
\caption{Summary of the biological datasets used for benchmarking.
All the datasets are Illumina reads.}
\begin{tabular}{l|l c r}
    \textit{dataset}   & \textit{read count} &
    \textit{read length} & \textit{type} \\ \hline
    dataset 1 & 16,457,527   & 50  & single      \\
    dataset 2 & 127,675,537  & 50  & single      \\
    dataset 3 & 2,460,226    & 100  & paired-end \\
\end{tabular}
\label{tab:biobench_properties}
\end{table}

@@

\begin{table}[h]
\centering
\caption{Running time (in seconds) of the software on three biological
datasets. Runs longer than 10 days were interrupted. A dash indicates
that the software cannot be used for this dataset.}
\begin{tabular}{l|c c c}
    \textit{software}   & \textit{dataset 1} &
      \textit{dataset 2} & \textit{dataset 3} \\ \hline
    starcode   & 171         & 2,898       & 44    \\
    seed       & 135,959     & 60,374      & -     \\
    sidesort   & 632,168     & $>$ 10 days & -     \\
    rainbow    & -           & -           & 306   \\
    cd-hit-est & $>$ 10 days & 512,591     & -     \\
\end{tabular}
\label{tab:biobench_runtime}
\end{table}

@@

\begin{table}[h]
\centering
\caption{Memory usage (in Gb).}
\begin{tabular}{l|c c c}
    \textit{software}   & \textit{dataset 1} &
      \textit{dataset 2} & \textit{dataset 3} \\ \hline
    starcode   & 9.4 & 30.9 & 5.2 \\
    seed       & 4.1 & 53.9 & -   \\
    sidesort   & 1.9 & 13.9 & -   \\
    rainbow    & -   & -  & 0.5   \\
    cd-hit-est & 3.8 & 28.5 & -   \\
\end{tabular}
\label{tab:biobench_memory}
\end{table}
